\Title

### 2021-07-15 manuscript/content.tex
Add a sentence about the interpolation error from CV
Review discussion once more (#163)
Going over the discussion and conclusions. Added some text about the Australia data application (some moved from the results).

The application of the gradient-boosted equivalent sources to the Australian
gravity dataset demonstrates that the method is able to interpolate and
upward-continue large datasets in a reasonable amount of time using only modest
computational resources.
The resulting grid (Fig.~\ref{fig:australia}) preserves the high resolution of
the original data while avoiding aliasing artifacts due to the block averaging
of the source locations.
Some parts of the grid are smoother and have lower amplitudes than the original
data (e.g., some southwestern parts), which is expected from the upward
continuation that was performed to have the grid at a constant height.

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
This work contains British Geological Survey materials ©~UKRI.

S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
results, and wrote the paper. S.R. Soler produced all results and developed the
software implementation with minor revisions by L. Uieda.

>>>>

The application of the gradient-boosted equivalent sources to the Australian
gravity dataset demonstrates that the method is able to interpolate and
upward-continue large datasets in a reasonable amount of time using only modest
computational resources.
The resulting grid (Fig.~\ref{fig:australia}) preserves the high resolution of
the original data while avoiding aliasing artifacts due to the block averaging
of the source locations.
Some parts of the grid are smoother and have lower amplitudes than the original
data (e.g., some southwestern parts), which is expected from the upward
continuation that was performed to have the grid at a constant height.
From the cross-validation analysis on a subset of the data, we estimate that
the interpolation error is approximately \AustraliaEqlRmsScore{}.

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
We would also like to thank Editor Frederik Simons, Assistant Editor Fern
Storey, and two anonymous reviewers for their constructive comments.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
This work contains British Geological Survey materials ©~UKRI.
S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
results, and wrote the paper. S.R. Soler produced all results and developed the
software implementation with the assistance of L. Uieda.
